---
title: "Analysis"
output: html_document
date: "2024"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Load the data 
```{r}
library(miceadds)
data <- do.call(rbind,lapply(paste0("sim_performance",c(1:50),".Rdata"), load.Rdata2))

attach(data)
```

## Check R-hats are all < 1.01 

```{r}
# R square prior 
summary(rhat_rsquare)

# Normal large SD prior  
summary(rhat_normal_largesd)

# Normal small SD prior 
summary(rhat_normal_smallsd)

# Laplace large SD prior 
summary(rhat_laplace_largesd)

# Laplace small SD prior 
summary(rhat_laplace_smallsd)

# Cauchy  
summary(rhat_cauchy)

```

## Check bulk ESS are sufficiently large (minimum 400, ideally above 1000)
```{r}
# R square prior 
summary(bulkess_rsquare)

# Normal large SD prior  
summary(bulkess_normal_largesd)

# Normal small SD prior 
summary(bulkess_normal_smallsd)

# Laplace large SD prior 
summary(bulkess_laplace_largesd)

# Laplace small SD prior 
summary(bulkess_laplace_smallsd)

# Cauchy  
summary(bulkess_cauchy)

```

## Check tail ESS are sufficiently large (should be >400, ideally above 1000)
```{r}
# R square prior 
summary(tailess_rsquare)

# Normal large SD prior  
summary(tailess_normal_largesd)

# Normal small SD prior 
summary(tailess_normal_smallsd)

# Laplace large SD prior 
summary(tailess_laplace_largesd)

# Laplace small SD prior 
summary(tailess_laplace_smallsd)

# Cauchy  
summary(tailess_cauchy)

```


## Check that the MCSE meets upper bound of 0.01 
```{r}
# R square prior 
summary(mcse_rsquare)

# Normal large SD prior  
summary(mcse_normal_largesd)

# Normal small SD prior 
summary(mcse_normal_smallsd)

# Laplace large SD prior 
summary(mcse_laplace_largesd)

# Laplace small SD prior 
summary(mcse_laplace_smallsd)

# Cauchy  
summary(mcse_cauchy)

```


## Check number of divergent transitions - this should be kept to a minimum if any (<10)
```{r}

# Normal large SD prior  
summary(numdivergent_normal_largesd)

# Normal small SD prior 
summary(numdivergent_normal_smallsd)

# Laplace large SD prior 
summary(numdivergent_laplace_largesd)

# Laplace small SD prior 
summary(numdivergent_laplace_smallsd)

# Cauchy  
summary(numdivergent_cauchy)

```

## Calculate performance measures 
## Bias across each model 
```{r}
bias_rsq <- mean(bias_rsquare)
bias_normlargesd <- mean(bias_normal_largesd)
bias_normsmallsd <- mean(bias_normal_smallsd)
bias_laplargesd <- mean(bias_laplace_largesd)
bias_lapsmallsd <- mean(bias_laplace_smallsd)
bias_cauch <- mean(bias_cauchy)
bias_frequentist <- mean(bias_freq)
```

## Relative bias across each model 
```{r}
relbias_rsq <- (exp(bias_rsq + log(1))-exp(log(1)))/(exp(log(1)))
relbias_normlargesd <- (exp(bias_normlargesd+ log(1))-exp(log(1)))/(exp(log(1)))
relbias_normsmallsd <- (exp(bias_normsmallsd+ log(1))-exp(log(1)))/(exp(log(1)))
relbias_laplargesd <- (exp(bias_laplargesd+ log(1))-exp(log(1)))/(exp(log(1)))
relbias_lapsmallsd <- (exp(bias_lapsmallsd+ log(1))-exp(log(1)))/(exp(log(1)))
relbias_cauchy <- (exp(bias_cauch+ log(1))-exp(log(1)))/(exp(log(1)))
relbias_frequentist <- (exp(bias_frequentist+ log(1))-exp(log(1)))/(exp(log(1)))
```


## Coverage across each model 
```{r}
coverage_rsq <- mean(coverage_rsquare)
coverage_normlargesd <- mean(coverage_normal_largesd)
coverage_normsmallsd <- mean(coverage_normal_smallsd)
coverage_laplargesd <- mean(coverage_laplace_largesd)
coverage_lapsmallsd <- mean(coverage_laplace_smallsd)
coverage_cauch <- mean(coverage_cauchy)
coverage_frequentist <- mean(coverage_freq)
```


## MSE across each model and cumulative logit 
```{r}
mse_rsq <- mean(mse_rsquare)
mse_normlargesd <- mean(mse_normal_largesd)
mse_normsmallsd <- mean(mse_normal_smallsd)
mse_laplargesd <- mean(mse_laplace_largesd)
mse_lapsmallsd <- mean(mse_laplace_smallsd)
mse_cauch <- mean(mse_cauchy)
mse_frequentist <- mean(mse_freq)
```


## Posterior probability of superiority 
```{r}
postprob_rsq <- mean(postprob_rsquare)
postprob_normlargesd <- mean(postprob_normal_largesd)
postprob_normsmallsd <- mean(postprob_normal_smallsd)
postprob_laplargesd <- mean(postprob_laplace_largesd)
postprob_lapsmallsd <- mean(postprob_laplace_smallsd)
postprob_cauch <- mean(postprob_cauchy)

## Proportion that declare superiority 
postsup_rsq <- mean(postprob_rsquare > 0.95)
postsup_normlargesd <- mean(postprob_normal_largesd > 0.95)
postsup_normsmallsd <- mean(postprob_normal_smallsd > 0.95)
postsup_laplargesd <- mean(postprob_laplace_largesd > 0.95)
postsup_lapsmallsd <- mean(postprob_laplace_smallsd > 0.95)
postsup_cauch <- mean(postprob_cauchy > 0.95)
```

## Compute jackknife-after-bootstrap Monte Carlo standard error estimation - BIAS 
## These should be <0.05, otherwise increase n_sim 
```{r}
nsim <- 1000

MC_YMinusi_bias_rsquare <- MC_YMinusi_bias_normlargesd <- MC_YMinusi_bias_normsmallsd <- MC_YMinusi_bias_laplargesd <- MC_YMinusi_bias_lapsmallsd <- MC_YMinusi_bias_cauch <- numeric(nsim)

for(i in 1:nsim){
  MC_YMinusi_bias_rsquare[i] = sum(bias_rsquare[-i])/(nsim-1)
  MC_YMinusi_bias_normlargesd[i] = sum(bias_normal_largesd[-i])/(nsim-1)
  MC_YMinusi_bias_normsmallsd[i] = sum(bias_normal_smallsd[-i])/(nsim-1)
  MC_YMinusi_bias_laplargesd[i] = sum(bias_laplace_largesd[-i])/(nsim-1)
  MC_YMinusi_bias_lapsmallsd[i] = sum(bias_laplace_smallsd[-i])/(nsim-1)
  MC_YMinusi_bias_cauch[i] = sum(bias_cauchy[-i])/(nsim-1)
}

bar_MC_YMinusi_bias_rsquare = sum(MC_YMinusi_bias_rsquare)/nsim
bar_MC_YMinusi_bias_normlargesd = sum(MC_YMinusi_bias_normlargesd)/nsim
bar_MC_YMinusi_bias_normsmallsd = sum(MC_YMinusi_bias_normsmallsd)/nsim
bar_MC_YMinusi_bias_laplargesd = sum(MC_YMinusi_bias_laplargesd)/nsim
bar_MC_YMinusi_bias_lapsmallsd = sum(MC_YMinusi_bias_lapsmallsd)/nsim
bar_MC_YMinusi_bias_cauch = sum(MC_YMinusi_bias_cauch)/nsim

MCE_JK_bias_rsquare = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_bias_rsquare-bar_MC_YMinusi_bias_rsquare)^2))
MCE_JK_bias_normlargesd = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_bias_normlargesd-bar_MC_YMinusi_bias_normlargesd)^2))
MCE_JK_bias_normsmallsd = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_bias_normsmallsd-bar_MC_YMinusi_bias_normsmallsd)^2))
MCE_JK_bias_laplargesd = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_bias_laplargesd-bar_MC_YMinusi_bias_laplargesd)^2))
MCE_JK_bias_lapsmallsd = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_bias_lapsmallsd-bar_MC_YMinusi_bias_lapsmallsd)^2))
MCE_JK_bias_cauch = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_bias_cauch-bar_MC_YMinusi_bias_cauch)^2))

```


## Compute jackknife-after-bootstrap Monte Carlo standard error estimation -  RELATIVE BIAS 
## These should be <0.05, otherwise increase n_sim 
```{r}
nsim <- 1000

MC_YMinusi_relbias_rsquare <- MC_YMinusi_relbias_normlargesd <- MC_YMinusi_relbias_normsmallsd <- MC_YMinusi_relbias_laplargesd <- MC_YMinusi_relbias_lapsmallsd <- MC_YMinusi_relbias_cauch <- numeric(nsim)

for(i in 1:nsim){
  MC_YMinusi_relbias_rsquare[i] = (exp(sum(bias_rsquare[-i])/(nsim-1)+ log(1))-exp(log(1)))/(exp(log(1)))
  MC_YMinusi_relbias_normlargesd[i] = (exp(sum(bias_normal_largesd[-i])/(nsim-1)+ log(1))-exp(log(1)))/(exp(log(1)))
  MC_YMinusi_relbias_normsmallsd[i] = (exp(sum(bias_normal_smallsd[-i])/(nsim-1)+ log(1))-exp(log(1)))/(exp(log(1)))
  MC_YMinusi_relbias_laplargesd[i] = (exp(sum(bias_laplace_largesd[-i])/(nsim-1)+ log(1))-exp(log(1)))/(exp(log(1)))
  MC_YMinusi_relbias_lapsmallsd[i] = (exp(sum(bias_laplace_smallsd[-i])/(nsim-1)+ log(1))-exp(log(1)))/(exp(log(1)))
  MC_YMinusi_relbias_cauch[i] = (exp(sum(bias_cauchy[-i])/(nsim-1)+ log(1))-exp(log(1)))/(exp(log(1)))
}


bar_MC_YMinusi_relbias_rsquare = sum(MC_YMinusi_relbias_rsquare)/nsim
bar_MC_YMinusi_relbias_normlargesd = sum(MC_YMinusi_relbias_normlargesd)/nsim
bar_MC_YMinusi_relbias_normsmallsd = sum(MC_YMinusi_relbias_normsmallsd)/nsim
bar_MC_YMinusi_relbias_laplargesd = sum(MC_YMinusi_relbias_laplargesd)/nsim
bar_MC_YMinusi_relbias_lapsmallsd = sum(MC_YMinusi_relbias_lapsmallsd)/nsim
bar_MC_YMinusi_relbias_cauch = sum(MC_YMinusi_relbias_cauch)/nsim

MCE_JK_relbias_rsquare = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_relbias_rsquare-bar_MC_YMinusi_relbias_rsquare)^2))
MCE_JK_relbias_normlargesd = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_relbias_normlargesd-bar_MC_YMinusi_relbias_normlargesd)^2))
MCE_JK_relbias_normsmallsd = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_relbias_normsmallsd-bar_MC_YMinusi_relbias_normsmallsd)^2))
MCE_JK_relbias_laplargesd = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_relbias_laplargesd-bar_MC_YMinusi_relbias_laplargesd)^2))
MCE_JK_relbias_lapsmallsd = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_relbias_lapsmallsd-bar_MC_YMinusi_relbias_lapsmallsd)^2))
MCE_JK_relbias_cauch = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_relbias_cauch-bar_MC_YMinusi_relbias_cauch)^2))

```

## Compute jackknife-after-bootstrap Monte Carlo standard error estimation - COVERAGE 
```{r}
nsim <- 1000

MC_YMinusi_cv_rsquare <- MC_YMinusi_cv_normlargesd <- MC_YMinusi_cv_normsmallsd <- MC_YMinusi_cv_laplargesd <- MC_YMinusi_cv_lapsmallsd <- MC_YMinusi_cv_cauch <- numeric(nsim)

for(i in 1:nsim){
  MC_YMinusi_cv_rsquare[i] = sum(coverage_rsquare[-i])/(nsim-1)
  MC_YMinusi_cv_normlargesd[i] = sum(coverage_normal_largesd[-i])/(nsim-1)
  MC_YMinusi_cv_normsmallsd[i] = sum(coverage_normal_smallsd[-i])/(nsim-1)
  MC_YMinusi_cv_laplargesd[i] = sum(coverage_laplace_largesd[-i])/(nsim-1)
  MC_YMinusi_cv_lapsmallsd[i] = sum(coverage_laplace_smallsd[-i])/(nsim-1)
  MC_YMinusi_cv_cauch[i] = sum(coverage_cauchy[-i])/(nsim-1)
}

bar_MC_YMinusi_cv_rsquare = sum(MC_YMinusi_cv_rsquare)/nsim
bar_MC_YMinusi_cv_normlargesd = sum(MC_YMinusi_cv_normlargesd)/nsim
bar_MC_YMinusi_cv_normsmallsd = sum(MC_YMinusi_cv_normsmallsd)/nsim
bar_MC_YMinusi_cv_laplargesd = sum(MC_YMinusi_cv_laplargesd)/nsim
bar_MC_YMinusi_cv_lapsmallsd = sum(MC_YMinusi_cv_lapsmallsd)/nsim
bar_MC_YMinusi_cv_cauch = sum(MC_YMinusi_cv_cauch)/nsim

MCE_JK_cv_rsquare = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_cv_rsquare-bar_MC_YMinusi_cv_rsquare)^2))
MCE_JK_cv_normlargesd = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_cv_normlargesd-bar_MC_YMinusi_cv_normlargesd)^2))
MCE_JK_cv_normsmallsd = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_cv_normsmallsd-bar_MC_YMinusi_cv_normsmallsd)^2))
MCE_JK_cv_laplargesd = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_cv_laplargesd-bar_MC_YMinusi_cv_laplargesd)^2))
MCE_JK_cv_lapsmallsd = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_cv_lapsmallsd-bar_MC_YMinusi_cv_lapsmallsd)^2))
MCE_JK_cv_cauch = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_cv_cauch-bar_MC_YMinusi_cv_cauch)^2))
```


## Compute jackknife-after-bootstrap Monte Carlo standard error estimation - MSE 
```{r}
nsim <- 1000

MC_YMinusi_mse_rsquare <- MC_YMinusi_mse_normlargesd <- MC_YMinusi_mse_normsmallsd <- MC_YMinusi_mse_laplargesd <- MC_YMinusi_mse_lapsmallsd <- MC_YMinusi_mse_cauch <- numeric(nsim)

for(i in 1:nsim){
  MC_YMinusi_mse_rsquare[i] = sum(mse_rsquare[-i])/(nsim-1)
  MC_YMinusi_mse_normlargesd[i] = sum(mse_normal_largesd[-i])/(nsim-1)
  MC_YMinusi_mse_normsmallsd[i] = sum(mse_normal_smallsd[-i])/(nsim-1)
  MC_YMinusi_mse_laplargesd[i] = sum(mse_laplace_largesd[-i])/(nsim-1)
  MC_YMinusi_mse_lapsmallsd[i] = sum(mse_laplace_smallsd[-i])/(nsim-1)
  MC_YMinusi_mse_cauch[i] = sum(mse_cauchy[-i])/(nsim-1)
}

bar_MC_YMinusi_mse_rsquare = sum(MC_YMinusi_mse_rsquare)/nsim
bar_MC_YMinusi_mse_normlargesd = sum(MC_YMinusi_mse_normlargesd)/nsim
bar_MC_YMinusi_mse_normsmallsd = sum(MC_YMinusi_mse_normsmallsd)/nsim
bar_MC_YMinusi_mse_laplargesd = sum(MC_YMinusi_mse_laplargesd)/nsim
bar_MC_YMinusi_mse_lapsmallsd = sum(MC_YMinusi_mse_lapsmallsd)/nsim
bar_MC_YMinusi_mse_cauch = sum(MC_YMinusi_mse_cauch)/nsim

MCE_JK_mse_rsquare = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_mse_rsquare-bar_MC_YMinusi_mse_rsquare)^2))
MCE_JK_mse_normlargesd = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_mse_normlargesd-bar_MC_YMinusi_mse_normlargesd)^2))
MCE_JK_mse_normsmallsd = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_mse_normsmallsd-bar_MC_YMinusi_mse_normsmallsd)^2))
MCE_JK_mse_laplargesd = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_mse_laplargesd-bar_MC_YMinusi_mse_laplargesd)^2))
MCE_JK_mse_lapsmallsd = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_mse_lapsmallsd-bar_MC_YMinusi_mse_lapsmallsd)^2))
MCE_JK_mse_cauch = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_mse_cauch-bar_MC_YMinusi_mse_cauch)^2))
```



## Compute jackknife-after-bootstrap Monte Carlo standard error estimation - posterior probability 
```{r}
nsim <- 1000

MC_YMinusi_postprob_rsquare <- MC_YMinusi_postprob_normlargesd <- MC_YMinusi_postprob_normsmallsd <- MC_YMinusi_postprob_laplargesd <- MC_YMinusi_postprob_lapsmallsd <- MC_YMinusi_postprob_cauch <- numeric(nsim)

for(i in 1:nsim){
  MC_YMinusi_postprob_rsquare[i] = sum(postprob_rsquare[-i])/(nsim-1)
  MC_YMinusi_postprob_normlargesd[i] = sum(postprob_normal_largesd[-i])/(nsim-1)
  MC_YMinusi_postprob_normsmallsd[i] = sum(postprob_normal_smallsd[-i])/(nsim-1)
  MC_YMinusi_postprob_laplargesd[i] = sum(postprob_laplace_largesd[-i])/(nsim-1)
  MC_YMinusi_postprob_lapsmallsd[i] = sum(postprob_laplace_smallsd[-i])/(nsim-1)
  MC_YMinusi_postprob_cauch[i] = sum(postprob_cauchy[-i])/(nsim-1)
}

bar_MC_YMinusi_postprob_rsquare = sum(MC_YMinusi_postprob_rsquare)/nsim
bar_MC_YMinusi_postprob_normlargesd = sum(MC_YMinusi_postprob_normlargesd)/nsim
bar_MC_YMinusi_postprob_normsmallsd = sum(MC_YMinusi_postprob_normsmallsd)/nsim
bar_MC_YMinusi_postprob_laplargesd = sum(MC_YMinusi_postprob_laplargesd)/nsim
bar_MC_YMinusi_postprob_lapsmallsd = sum(MC_YMinusi_postprob_lapsmallsd)/nsim
bar_MC_YMinusi_postprob_cauch = sum(MC_YMinusi_postprob_cauch)/nsim

MCE_JK_postprob_rsquare = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_postprob_rsquare-bar_MC_YMinusi_postprob_rsquare)^2))
MCE_JK_postprob_normlargesd = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_postprob_normlargesd-bar_MC_YMinusi_postprob_normlargesd)^2))
MCE_JK_postprob_normsmallsd = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_postprob_normsmallsd-bar_MC_YMinusi_postprob_normsmallsd)^2))
MCE_JK_postprob_laplargesd = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_postprob_laplargesd-bar_MC_YMinusi_postprob_laplargesd)^2))
MCE_JK_postprob_lapsmallsd = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_postprob_lapsmallsd-bar_MC_YMinusi_postprob_lapsmallsd)^2))
MCE_JK_postprob_cauch = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_postprob_cauch-bar_MC_YMinusi_postprob_cauch)^2))
```



## Compute jackknife-after-bootstrap Monte Carlo standard error estimation - proportion declaring superiority 
```{r}
nsim <- 1000

MC_YMinusi_postsup_rsquare <- MC_YMinusi_postsup_normlargesd <- MC_YMinusi_postsup_normsmallsd <- MC_YMinusi_postsup_laplargesd <- MC_YMinusi_postsup_lapsmallsd <- MC_YMinusi_postsup_cauch <- numeric(nsim)

for(i in 1:nsim){
  MC_YMinusi_postsup_rsquare[i] = sum(postprob_rsquare[-i] > 0.95)/(nsim-1)
  MC_YMinusi_postsup_normlargesd[i] = sum(postprob_normal_largesd[-i] > 0.95)/(nsim-1)
  MC_YMinusi_postsup_normsmallsd[i] = sum(postprob_normal_smallsd[-i] > 0.95)/(nsim-1)
  MC_YMinusi_postsup_laplargesd[i] = sum(postprob_laplace_largesd[-i] > 0.95)/(nsim-1)
  MC_YMinusi_postsup_lapsmallsd[i] = sum(postprob_laplace_smallsd[-i] > 0.95)/(nsim-1)
  MC_YMinusi_postsup_cauch[i] = sum(postprob_cauchy[-i] > 0.95)/(nsim-1)
}

bar_MC_YMinusi_postsup_rsquare = sum(MC_YMinusi_postsup_rsquare)/nsim
bar_MC_YMinusi_postsup_normlargesd = sum(MC_YMinusi_postsup_normlargesd)/nsim
bar_MC_YMinusi_postsup_normsmallsd = sum(MC_YMinusi_postsup_normsmallsd)/nsim
bar_MC_YMinusi_postsup_laplargesd = sum(MC_YMinusi_postsup_laplargesd)/nsim
bar_MC_YMinusi_postsup_lapsmallsd = sum(MC_YMinusi_postsup_lapsmallsd)/nsim
bar_MC_YMinusi_postsup_cauch = sum(MC_YMinusi_postsup_cauch)/nsim

MCE_JK_postsup_rsquare = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_postsup_rsquare-bar_MC_YMinusi_postsup_rsquare)^2))
MCE_JK_postsup_normlargesd = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_postsup_normlargesd-bar_MC_YMinusi_postsup_normlargesd)^2))
MCE_JK_postsup_normsmallsd = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_postsup_normsmallsd-bar_MC_YMinusi_postsup_normsmallsd)^2))
MCE_JK_postsup_laplargesd = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_postsup_laplargesd-bar_MC_YMinusi_postsup_laplargesd)^2))
MCE_JK_postsup_lapsmallsd = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_postsup_lapsmallsd-bar_MC_YMinusi_postsup_lapsmallsd)^2))
MCE_JK_postsup_cauch = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_postsup_cauch-bar_MC_YMinusi_postsup_cauch)^2))
```


## Compute jackknife-after-bootstrap Monte Carlo standard error estimation - proportion declaring superiority 
```{r}
nsim <- 1000

MC_YMinusi_stopearly_rsquare <- MC_YMinusi_stopearly_normlargesd <- MC_YMinusi_stopearly_normsmallsd <- MC_YMinusi_stopearly_laplargesd <- MC_YMinusi_stopearly_lapsmallsd <- MC_YMinusi_stopearly_cauch <- numeric(nsim)

for(i in 1:nsim){
  MC_YMinusi_stopearly_rsquare[i] = sum(stopping_rsquare[-i])/(nsim-1)
  MC_YMinusi_stopearly_normlargesd[i] = sum(stopping_normal_largesd[-i])/(nsim-1)
  MC_YMinusi_stopearly_normsmallsd[i] = sum(stopping_normal_smallsd[-i])/(nsim-1)
  MC_YMinusi_stopearly_laplargesd[i] = sum(stopping_laplace_largesd[-i])/(nsim-1)
  MC_YMinusi_stopearly_lapsmallsd[i] = sum(stopping_laplace_smallsd[-i])/(nsim-1)
  MC_YMinusi_stopearly_cauch[i] = sum(stopping_cauchy[-i])/(nsim-1)
}

bar_MC_YMinusi_stopearly_rsquare = sum(MC_YMinusi_stopearly_rsquare)/nsim
bar_MC_YMinusi_stopearly_normlargesd = sum(MC_YMinusi_stopearly_normlargesd)/nsim
bar_MC_YMinusi_stopearly_normsmallsd = sum(MC_YMinusi_stopearly_normsmallsd)/nsim
bar_MC_YMinusi_stopearly_laplargesd = sum(MC_YMinusi_stopearly_laplargesd)/nsim
bar_MC_YMinusi_stopearly_lapsmallsd = sum(MC_YMinusi_stopearly_lapsmallsd)/nsim
bar_MC_YMinusi_stopearly_cauch = sum(MC_YMinusi_stopearly_cauch)/nsim

MCE_JK_stopearly_rsquare = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_stopearly_rsquare-bar_MC_YMinusi_stopearly_rsquare)^2))
MCE_JK_stopearly_normlargesd = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_stopearly_normlargesd-bar_MC_YMinusi_stopearly_normlargesd)^2))
MCE_JK_stopearly_normsmallsd = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_stopearly_normsmallsd-bar_MC_YMinusi_stopearly_normsmallsd)^2))
MCE_JK_stopearly_laplargesd = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_stopearly_laplargesd-bar_MC_YMinusi_stopearly_laplargesd)^2))
MCE_JK_stopearly_lapsmallsd = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_stopearly_lapsmallsd-bar_MC_YMinusi_stopearly_lapsmallsd)^2))
MCE_JK_stopearly_cauch = sqrt(((nsim-1)/nsim)*sum((MC_YMinusi_stopearly_cauch-bar_MC_YMinusi_stopearly_cauch)^2))

stopearly_se <- c(MCE_JK_stopearly_rsquare,MCE_JK_stopearly_normlargesd,MCE_JK_stopearly_normsmallsd,MCE_JK_stopearly_laplargesd,MCE_JK_stopearly_lapsmallsd,MCE_JK_stopearly_cauch,NA)
```

## Generate data frame - bias, SE, coverage, SE, MSE, SE, rel bias, SE, post prob, SE, post sup, SE, model prior, etc
```{r}
bias <- c(bias_rsq, bias_normlargesd, bias_normsmallsd, bias_laplargesd, bias_lapsmallsd, bias_cauch, bias_frequentist)

bias_se <- c(MCE_JK_bias_rsquare, MCE_JK_bias_normlargesd, MCE_JK_bias_normsmallsd, MCE_JK_bias_laplargesd, MCE_JK_bias_lapsmallsd, MCE_JK_bias_cauch, NA)

relbias <- c(relbias_rsq, relbias_normlargesd, relbias_normsmallsd, relbias_laplargesd, relbias_lapsmallsd, relbias_cauchy, relbias_frequentist)

relbias_se <- c(MCE_JK_relbias_rsquare, MCE_JK_relbias_normlargesd, MCE_JK_relbias_normsmallsd, MCE_JK_relbias_laplargesd, MCE_JK_relbias_lapsmallsd, MCE_JK_relbias_cauch, NA)

coverage <- c(coverage_rsq, coverage_normlargesd, coverage_normsmallsd, coverage_laplargesd, coverage_lapsmallsd, coverage_cauch, coverage_frequentist)

coverage_se <- c(MCE_JK_cv_rsquare, MCE_JK_cv_normlargesd, MCE_JK_cv_normsmallsd, MCE_JK_cv_laplargesd, MCE_JK_cv_lapsmallsd, MCE_JK_cv_cauch, NA)

mse <- c(mse_rsq, mse_normlargesd, mse_normsmallsd, mse_laplargesd, mse_lapsmallsd, mse_cauch, mse_frequentist)

mse_se <- c(MCE_JK_mse_rsquare, MCE_JK_mse_normlargesd, MCE_JK_mse_normsmallsd, MCE_JK_mse_laplargesd, MCE_JK_mse_lapsmallsd, MCE_JK_mse_cauch, NA)

postprob <- c(postprob_rsq, postprob_normlargesd, postprob_normsmallsd, postprob_laplargesd, postprob_lapsmallsd, postprob_cauch, NA)

postprob_se <- c(MCE_JK_postprob_rsquare, MCE_JK_postprob_normlargesd, MCE_JK_postprob_normsmallsd, MCE_JK_postprob_laplargesd, MCE_JK_postprob_lapsmallsd, MCE_JK_postprob_cauch, NA)

postsup <- c(postsup_rsq, postsup_normlargesd, postsup_normsmallsd, postsup_laplargesd, postsup_lapsmallsd, postsup_cauch, NA)

postsup_se <- c(MCE_JK_postsup_rsquare, MCE_JK_postsup_normlargesd, MCE_JK_postsup_normsmallsd, MCE_JK_postsup_laplargesd, MCE_JK_postsup_lapsmallsd, MCE_JK_postsup_cauch, NA)

model <- c(rep("R-square",1),rep("Normal - large SD",1),rep("Normal - small SD",1),rep("Laplace - large SD",1),rep("Laplace - small SD",1), rep("Cauchy",1), rep("Frequentist",1))

stopping <- c( mean(stopping_rsquare),mean(stopping_normal_largesd), mean(stopping_normal_smallsd), mean(stopping_laplace_largesd), mean(stopping_laplace_smallsd), mean(stopping_cauchy),  mean(stopping_freq))

category <- rep(30,7)

effectsize <- rep("None [OR = 1.00]", 7)

controlprob <- rep("Skewed", 7)

sampsize <- rep(500, 7)

design <- rep("Adaptive", 7)

prior <- rep("Beta", 7)

results <- data.frame(bias = bias, bias_se = bias_se, relbias = relbias, relbias_se = relbias_se, coverage = coverage, coverage_se = coverage_se, mse = mse, mse_se = mse_se, postprob = postprob, postprob_se = postprob_se, postsup = postsup, postsup_se = postsup_se, model = model, category = category, effectsize = effectsize, controlprob = controlprob, sampsize = sampsize, design = design, prior = prior, stopping = stopping, stopping_se = stopearly_se)

save(results, file = "results.Rdata")
write.csv(results,file="G:/BACKUP/Chris/Project_3/Main_Simulations/Results/results_73.csv")
```
